\documentclass[sigconf, review, anonymous]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
\setcopyright{rightsretained}

%Conference
\acmConference[ESEC/FSE 2018]{The 26th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{4–9 November, 2018}{Lake Buena Vista, Florida, United States}

\begin{document}
\title{Bug Report Classification using LSTM and CNN for More Accurate Software Defect Locating}

\author{Xin Ye}
\affiliation{%
  \institution{California State University San Marcos}
  \streetaddress{333 N Twin Oaks Valley Rd}
  \city{San Marcos}
  \state{California}
  \postcode{92069}
}
\email{xye@csusm.com}

\author{Fan Fang}
\affiliation{%
  \institution{California State University San Marcos}
  \streetaddress{333 N Twin Oaks Valley Rd}
  \city{San Marcos}
  \state{California}
  \postcode{92069}
}
\email{fang014@cougars.csusm.edu}

\author{Bartosh Sudak}
\affiliation{%
  \institution{California State University San Marcos}
  \streetaddress{333 N Twin Oaks Valley Rd}
  \city{San Marcos}
  \state{California}
  \postcode{92069}
}
\email{bartoshsudak@gmail.com}

\author{John Wu}
\affiliation{%
  \institution{California State University San Marcos}
  \streetaddress{333 N Twin Oaks Valley Rd}
  \city{San Marcos}
  \state{California}
  \postcode{92069}
}
\email{wu028@cougars.csusm.edu}

\author{Hui Shen}
\affiliation{%
  \institution{Ohio University}
  \city{Athens}
  \state{Ohio}
  \postcode{45701}
}
\email{hs138609@ohio.edu}

\author{Razvan Bunescu}
\affiliation{%
  \institution{Ohio University}
  \city{Athens}
  \state{Ohio}
  \postcode{45701}
}
\email{bunescu@ohio.edu}

\author{Chang Liu}
\affiliation{%
  \institution{Ohio University}
  \city{Athens}
  \state{Ohio}
  \postcode{45701}
}
\email{liuc@ohio.edu}

\begin{abstract}
The PI proposes a two-year project to develop an interactive and practical system that locates software defects automatically. This system will alleviate developers' effort in bug finding and improve productivity. In preliminary work, the PI developed a ranking model that ranks all the source code files for a given bug report. A source file at a higher position in the ranked list is more likely to contain defects than a source file at a lower position. The proposed system is an extension of the PI's preliminary work. In this project, the PI propose to 1) introduce a pre-filtering technique to filter out low-quality bug reports; 2) use artificial neural network to measure semantic relationship between bug reports and source code files; 3) implement an interactive 3-D VR user interface on multiple platforms for the system. The first two objectives aim at making the system be more accurate. The third objective aims at making the system be more usable. The PI propose to recruit two student assistants including one graduate and one undergraduate to help develop the system and perform experimental evaluation. The system will be published and will be used in the software engineering (SE) courses at California Sate University San Marcos to help students learn SE concepts in a lively manner.

This project will result in an interactive and practical system that can be used by the public. To increase system accuracy, this project proposes using artificial neural networks (ANNs) to classify bug reports into either ``predictable'' or ``unpredictable'', where ``unpredictable'' refers to low-quality reports that do not contain sufficient information for locating the bug. The system works on ``predictable'' reports and keeps silent on ``unpredictable'' reports. Besides, this project proposes using ANNs to measure the semantic similarity between a bug report and a source file. This semantic similarity is used as a new feature that complements other lexical-similarity features. To make the system be usable, this project proposes to develop an interactive user interface on multiple platforms. Furthermore, this project proposes to develop a supplemental and selectable 3-D VR visualization module that helps developers understand the code change history more efficiently.

This project will publish a practical defect positioning system that can be used in both academic and industry. The research outcome will provide the basis for the PI's future work. The methodology and techniques used in this project will contribute to the software engineering (SE) community in similar work. The funding to this project will help the PI build an SE lab and found an SE research group at California State University San Marcos (CSUSM). The research lab will provide students with the necessary computing resources for doing SE research projects. The research group will expose students to new SE techniques and research projects. The funding to this project will also help provide paid positions and new opportunities to our students that have strong desire in doing research projects.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257.10010258.10010259.10010263</concept_id>
<concept_desc>Computing methodologies~Supervised learning by classification</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003317.10003371.10003381.10003385</concept_id>
<concept_desc>Information systems~Multilingual and cross-lingual retrieval</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Supervised learning by classification}
\ccsdesc[500]{Software and its engineering~Software testing and debugging}
\ccsdesc[300]{Information systems~Multilingual and cross-lingual retrieval}


\keywords{Recurrent neural network, long short-term memory, convolutional neural network, bug localization, bug report}


\maketitle

\input{sections/introduction}
\input{sections/related-work}
\input{sections/future-work}
\input{sections/conclusion}
\input{sections/acknowledgement}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}
